Behavioral Analysis of the Agent-Based Community Grid Solution for the Large Hadron Collider beauty Experiment

### 2011-11-13 paper_update.tex
chapter 3 done

$ _{.RPAgent; }$
$ \\ $

%Since the services are the frontend for all interractions with the storage,
%they essentially act as wrappers around the storage. By already modeling
%the storage as a recursive process with memory, there is no need to model them explicitely.

Thus, so far we have established: a) a finite domain of abstract values, b) an
abstraction for mapping concrete program values to abstract ones and
c) collection of processes built from parametrized actions describing 
the behavior of the program components.
Substituting concrete operations on real data of interest
with the corresponding operations of the abstract interpretation yields 
our abstract model. Finally, the model is put together as a parallel composition of all
communicating processes.

>>>>

$ _{.RPAgent; }$
$ \\ $
%Since the services are the frontend for all interractions with the storage,
%they essentially act as wrappers around the storage. By already modeling
%the storage as a recursive process with memory, there is no need to model them explicitely. 
Finally, the model is put together as a parallel composition of all
communicating processes.

We have established general modeling guidelines and illustrated them
on the SMS subsystem. Although the WMS model is larger, it is obtained using the same approach.
The complete models are available at \cite{svn_mcrl2}.
